MSK IV

### 2017-07-27 msk4.rmd
re-added

>>>>

## Trigger 1

Ulcer: local defect of tissue or organ caused by sloughing of inflammatory or necrotic material.

Pathogenesis of ulcer formation: possibly from kicking the bed, then repetitive trauma.

Factors preventing ulcer from healing (learn this):

-  Infn
-  Smoking
-  *Old* age
-  Heavy alcohol consumption
-  Medication: steroids, NSAIDs
-  Obesity
-  Repetitive trauma
-  Diabetic: due to decreased blood flow, increased risk for infn due to high sugar, neuropathy
-  Vascular disease (oxygen supply)
-  Poor hygiene + improper wound care
-  Malnutrition
-  Super rare genetic diseases

Wound present for long time:

-  Can affect gait/joints
-  Osteomyelitis
-  Scar
-  Could turn malignant (if wound not healing, always biopsy it)
